\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{times} % Time New Roman
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue]{hyperref}

% Section spacing
\usepackage{titlesec}
\titlespacing\section{0pt}{6pt}{6pt}
\titleformat{\section}{\normalfont\fontsize{12}{12}\bfseries}{\thesection}{1em}{}

% Custom list
\usepackage{enumitem}
\setlist{nosep}
\newlist{cvlist}{description}{1}
\setlist[cvlist]{style=sameline,leftmargin=1in,font=\normalfont,itemsep=2pt}
\setcounter{secnumdepth}{0}

% Help line breaks
\sloppy

\begin{document}

\begin{center}
\textbf{Nicholas Wogan}

SETI Institute \& NASA Ames Research Center

Email: nicholaswogan@gmail.com or nicholas.f.wogan@nasa.gov

GitHub: \url{https://github.com/Nicholaswogan}

Date generated: \today

\end{center}

\section{Education \& Work Experience}

\begin{cvlist}
\item[2025 - pres.]
  Research Scientist, NASA Ames Research Center contracted via the SETI Institute, Moffett Field, CA.
\item[2023 - 2025]
  NASA Postdoctoral Program Fellow, Space Science and Astrobiology Division, NASA Ames Research Center, Moffett Field, CA. Advisor: Natasha Batalha.
\item[2017 - 2023]
  PhD Graduate Student, Dual-title Earth and Space Science and Astrobiology, University of Washington, Seattle, WA. Advisor: David Catling.
\item[2012 - 2016]
  B.S., Physics major, University of Oregon Honors College, Eugene, OR.
\end{cvlist}

\section{Awards \& Honors}

\begin{cvlist}
\item[2023]
  The David A. Johnston Award for Research Excellence, Earth and Space Science Department, University of Washington.
\item[2023] 
  NASA Postdoctoral Program Fellowship recipient
\item[2023]
  Award for best graphic in presentation, Earth and Space Science Gala, University of Washington.
\item[2017]
  Department of Earth and Space Sciences Top Scholar Award, University of Washington
\item[2016]
  Undergraduate Research Award, University of Oregon Physics department
\item[2016]
  Undergraduate Honors Thesis: Passed with Highest Distinction, University of Oregon Honors College
\end{cvlist}

\section{Mentoring, Teaching \& Outreach}

\begin{cvlist}
\item[2024 - pres.]
  Informally mentoring and collaborating with Conner Metz, a U-M graduate student, studying the photochemistry of sulfur on early Mars.
\item[2024 - pres.]
  Informally mentoring and collaborating with Sander Somers, a UMD graduate student, studying photochemical haze production in gas rich exoplanet atmospheres.
\item[2024 - pres.]
  Informally mentoring and collaborating with Samantha Gilbert, a UW graduate student, studying the coupled atmosphere-interior evolution of habitable rocky exoplanets.
\item[2024 - pres.]
  Informally mentoring and collaborating with John Herring, an ISU graduate student, studying the evolution of nitrogen on early Earth and rocky exoplanets.
\item[2025 - pres.]
  Mentoring Jaden Lopez, an undergraduate student at UCSC, through the Lamat Program. Jaden is studying gas opacities for the use of reflected light exoplanet spectroscopy.
\item[2025]
  Mentored Elizabeth Pawelka, a post-baccalaureate researcher, through the NASA OSTEM program. Elizabeth studied sub-Neptune atmospheres in the context of the Habitable Worlds Observatory.
\item[2024 - 2025]
  Informally mentored Sagnick Mukherjee, a former UCSC graduate student, on a first author article that studies photochemistry in hot gas giant atmospheres.
\item[2024 - 2025]
  Informally mentored Jea Adams Redai, a Harvard graduate student, on a first author article publishing JWST observations of the rocky exoplanet GJ 357 b.
\item[2024]
  Mentored Zoe Lu and Divya Bhamidipati, both high school students, through the NASA-Chabot internship program.
\item[2022 - 2023]
  ``Rockin' Out'' volunteer. Rockin' Out is a K-12 volunteer-based outreach program at the Department of Earth and Space Sciences at the University of Washington.
\item[2022]
  Presented at Astronomy on Tap, Seattle: ``How Life Started and Where The Universe Will Go''
\item[2019]
  Graduate Teaching Assistant: Intro. Astrobiology (ASTBIO 115; Winter), University of Washington.
\item[2018]
  Teaching Assistant: Intro. Geology (ESS 101; Winter), University of Washington.
\end{cvlist}

\section{Peer-Reviewed Publications}

\noindent 31 total, 7 first-author. Google Scholar: \href{https://scholar.google.com/citations?hl=en&user=BExg34IAAAAJ}{Linked here}. $^*$ indicates mentored graduate student. \\

\noindent Under Review

\begin{cvlist}
\item[2025]
  Joshua Krissansen-Totton, ..., \textbf{Nicholas Wogan} et al. (2025). Wavelength Requirements for Life Detection via Reflected Light Spectroscopy of Rocky Exoplanets. Under Review, \emph{Astrobiology}. \href{https://doi.org/10.48550/arXiv.2507.14771}{DOI: 10.48550/arXiv.2507.14771}.
\item[2025]
  Jegug Ih, ..., \textbf{Nicholas Wogan} et al. (2025). Do Rocky Planets around M Stars Have Atmospheres? A Statistical Approach to the Cosmic Shoreline. Under Review, \emph{AAS Journals}. \href{https://doi.org/10.48550/arXiv.2508.08253}{DOI: 10.48550/arXiv.2508.08253}.
\end{cvlist}

\noindent Accepted or Published

\begin{cvlist}
\item[2025]
  Sukrit Ranjan, \textbf{Nicholas Wogan} et al. (2025). The Photochemical Plausibility of Warm Exo-Titans Orbiting M-Dwarf Stars. Accepted, \emph{The Astrophysical Journal}. \href{https://doi.org/10.48550/arXiv.2509.10611}{DOI: 10.48550/arXiv.2509.10611}.
\item[2025]
  Am{\'e}lie Gressier, Natasha Batalha, \textbf{Nicholas Wogan} et al. (2025). JWST-TST DREAMS: Sulfur dioxide in the atmosphere of the Neptune-mass planet HAT-P-26 b from NIRSpec G395H transmission spectroscopy. Accepted, \emph{Astronomical Journal}. \href{https://doi.org/10.48550/arXiv.2509.16082}{DOI: 10.48550/arXiv.2509.16082}.
\item[2025]
  \textbf{Nicholas Wogan}, Natasha Batalha, Kevin Zahnle, Joshua Krissansen-Totton, David Catling, Eric Wolf, Tyler Robinson, Victoria Meadows, Giada Arney and Shawn Domagal-Goldman (2025). The Open-Source \texttt{Photochem} Code: A General Chemical and Climate Model for Interpreting (Exo)Planet Observations. Accepted, \emph{The Planetary Science Journal}. \href{https://doi.org/10.48550/arXiv.2509.25578}{DOI: 10.48550/arXiv.2509.25578}.
\item[2025]
  Stephen Schmidt, Ryan MacDonald, ..., \textbf{Nicholas Wogan} et al. (2025). A Comprehensive Reanalysis of K2-18 b's JWST NIRISS+NIRSpec Transmission Spectrum. Accepted, \emph{The Astronomical Journal}. \href{https://doi.org/10.48550/arXiv.2501.18477}{DOI: 10.48550/arXiv.2501.18477}.
\item[2025]
  Jea Adams Redai$^*$, \textbf{Nicholas Wogan} et al. (2025). JWST COMPASS: A NIRSpec G395H Transmission Spectrum of the Super-Earth GJ 357 b. \emph{The Astronomical Journal}. \href{https://doi.org/10.3847/1538-3881/adee92}{DOI: 10.3847/1538-3881/adee92}.
\item[2025]
  Trent Thomas$^*$, ..., \textbf{Nicholas Wogan} et al. (2025). Statistical Geochemical Constraints on Present-day Water Outgassing as a Source of Secondary Atmospheres on the TRAPPIST-1 Exoplanets. \emph{The Planetary Science Journal}. \href{https://doi.org/10.3847/PSJ/add261}{DOI: 10.3847/PSJ/add261}.
\item[2025]
  Sagnick Mukherjee$^*$, Jonathan Fortney, \textbf{Nicholas Wogan}, David Sing, and Kazumasa Ohno (2025). Effects of Planetary Parameters on Disequilibrium Chemistry in Irradiated Planetary Atmospheres: From Gas Giants to Sub-Neptunes. \emph{The Astrophysical Journal}. \href{https://doi.org/10.3847/1538-4357/adc7b3}{DOI: 10.3847/1538-4357/adc7b3}.
% \item[2025]
%   \textbf{Nicholas Wogan}, James Mang, Natasha Batalha et al. (2025). The Sonora Substellar Atmosphere Models. V. A Correction to the Disequilibrium Abundance of CO$_2$ for Sonora Elf Owl. \emph{RNAAS}. \href{https://doi.org/10.3847/2515-5172/add407}{DOI: 10.3847/2515-5172/add407}.
\item[2025]
  Kenneth Gordon, Theodora Karalidi, Kimberly Bott, \textbf{Nicholas Wogan} et al. (2025). Polarized Signatures of the Earth Through Time: An Outlook for the Habitable Worlds Observatory. \emph{The Astrophysical Journal}. \href{https://doi.org/10.3847/1538-4357/adc09c}{DOI: 10.3847/1538-4357/adc09c}.
\item[2025]
  Johanna Teske, Natasha Batalha, Nicole Wallack, James Kirk, \textbf{Nicholas Wogan} et al. (2025). JWST COMPASS: NIRSpec/G395H Transmission Observations of TOI-776 c, a 2 Rearth M Dwarf Planet. \emph{The Astronomical Journal}. \href{https://doi.org/10.3847/1538-3881/adb975}{DOI: 10.3847/1538-3881/adb975}.
\item[2025]
  Lili Alderson, Sarah Moran, Nicole Wallack, Natasha Batalha, \textbf{Nicholas Wogan} et al. (2025). JWST COMPASS: NIRSpec/G395H Transmission Observations of the Super-Earth TOI-776 b. \emph{The Astronomical Journal}. \href{https://doi.org/10.3847/1538-3881/adad64}{DOI: 10.3847/1538-3881/adad64}.
\item[2024]
  Nicholas Scarsdale, \textbf{Nicholas Wogan} et al. (2024). JWST COMPASS: The 3-5 $\mu$m Transmission Spectrum of the Super-Earth L 98-59 c. \emph{The Astronomical Journal}. \href{https://doi.org/10.3847/1538-3881/ad73cf}{DOI: 10.3847/1538-3881/ad73cf}.
\item[2024]
  Munazza Alam, Peter Gao, Jea Adams Redai, Nicole Wallack, \textbf{Nicholas Wogan} et al. (2024). JWST COMPASS: The First Near- to Mid-infrared Transmission Spectrum of the Hot Super-Earth L 168-9 b. \emph{The Astronomical Journal}. \href{https://doi.org/10.3847/1538-3881/ad8eb5}{DOI: 10.3847/1538-3881/ad8eb5}.
\item[2024]
  \textbf{Nicholas Wogan}, David Catling, and Kevin Zahnle (2024). Timing and likelihood of the origin of life derived from post-impact highly reducing atmospheres. \emph{Astrobiology}. \href{https://doi.org/10.1089/ast.2023.0128}{DOI: 10.1089/ast.2023.0128}.
\item[2024]
  Joshua Krissansen-Totton, \textbf{Nicholas Wogan}, Maggie Thompson and Jonathan Fortney (2024). The erosion of large primary atmospheres typically leaves behind substantial secondary atmospheres on temperate rocky planets. \emph{Nature Communications}. \href{https://doi.org/10.1038/s41467-024-52642-6}{DOI: 10.1038/s41467-024-52642-6}.
\item[2024]
  Nicole Wallack, Natasha Batalha, ..., \textbf{Nicholas Wogan} et al. (2024). JWST COMPASS: A NIRSpec/G395H Transmission Spectrum of the Sub-Neptune TOI-836c. \emph{The Astronomical Journal}. \href{https://doi.org/10.3847/1538-3881/ad3917}{DOI: 10.3847/1538-3881/ad3917}.
\item[2024]
  Lili Alderson, Natasha Batalha, ..., \textbf{Nicholas Wogan} et al. (2024). JWST COMPASS: NIRSpec/G395H Transmission Observations of the Super-Earth TOI-836b. \emph{The Astronomical Journal}. \href{https://doi.org/10.3847/1538-3881/ad32c9}{DOI: 10.3847/1538-3881/ad32c9}.
\item[2024]
  Shang-Min Tsai, Hamish Innes, \textbf{Nicholas Wogan}, Edward Schwieterman (2024). Biogenic Sulfur Gases as Biosignatures on Temperate Sub-Neptune Waterworlds. \emph{Astrophysical Journal Letters}. \href{https://doi.org/10.3847/2041-8213/ad3801}{DOI: 10.3847/2041-8213/ad3801}.
\item[2024]
  \textbf{Nicholas Wogan}, Natasha Batalha, Kevin Zahnle, Joshua Krissansen-Totton, Shang-Min Tsai, and Renyu Hu (2024). JWST observations of K2-18b can be explained by a gas-rich mini-Neptune with no habitable surface. \emph{Astrophysical Journal Letters}. \href{https://doi.org/10.3847/2041-8213/ad2616}{DOI: 10.3847/2041-8213/ad2616}.
\item[2024]
  Zoe Todd, \textbf{Nicholas Wogan}, and David Catling (2024). Favorable Environments for the Formation of Ferrocyanide, a Potentially Critical Reagent for Origins of Life. \emph{ACS Earth and Space Chemistry}. \href{https://doi.org/10.1021/acsearthspacechem.3c00213}{DOI: 10.1021/acsearthspacechem.3c00213}.
\item[2024]
  Amber Young, Tyler Robinson, Joshua Krissansen-Totton, Edward Schwieterman, \textbf{Nicholas Wogan} et al. (2024). Inferring chemical disequilibrium biosignatures for Proterozoic Earth-like exoplanets. \emph{Nature Astronomy}. \href{https://doi.org/10.1038/s41550-023-02145-z}{DOI: 10.1038/s41550-023-02145-z}.
\item[2023]
  \textbf{Nicholas Wogan}, David Catling, Kevin Zahnle, and Roxana Lupu (2023). Origin of life molecules in the atmosphere after big impacts on the early Earth. \emph{Planetary Science Journal}. \href{https://doi.org/10.3847/PSJ/aced83}{DOI: 10.3847/PSJ/aced83}.
\item[2023]
  Zachary Cohen, Zoe Todd, \textbf{Nicholas Wogan}, Roy Black, Sarah Keller, and David Catling (2023). Plausible sources of membrane-forming fatty acids on the early Earth: a review of the literature and an estimation of amounts. \emph{ACS Earth and Space Chemistry}. \href{https://doi.org/10.1021/acsearthspacechem.2c00168}{DOI: 10.1021/acsearthspacechem.2c00168}.
\item[2022]
  \textbf{Nicholas Wogan}, David Catling, Kevin Zahnle, and Mark Claire (2022). Rapid timescale for an oxic transition during the Great Oxidation Event and the instability of low atmospheric O$_2$. \emph{Proceedings of the National Academy of Sciences}. \href{https://doi.org/10.1073/pnas.2205618119}{DOI: 10.1073/pnas.2205618119}.
\item[2022]
  Maggie Thompson, Joshua Krissansen-Totton, \textbf{Nicholas Wogan}, Myriam Telus, and Jonathan Fortney (2022). The case and context for atmospheric methane as an exoplanet biosignature. \emph{Proceedings of the National Academy of Sciences}. \href{https://doi.org/10.1073/pnas.2117933119}{DOI: 10.1073/pnas.2117933119}.
\item[2021]
  Joshua Krissansen-Totton, Max Galloway, \textbf{Nicholas Wogan}, Jasmeet Dhaliwal, and Jonathan Fortney (2021). Waterworlds probably do not experience magmatic outgassing. \emph{The Astrophysical Journal}. \href{https://doi.org/10.3847/1538-4357/abf560}{DOI: 10.3847/1538-4357/abf560}.
\item[2021]
  Joshua Krissansen-Totton, Jonathan Fortney, Francis Nimmo, and \textbf{Nicholas Wogan}. Oxygen false positives on habitable zone planets around Sun-like stars. \emph{AGU Advances}. \href{https://doi.org/10.1029/2020AV000294}{DOI: 10.1029/2020AV000294}.
\item[2020]
  \textbf{Nicholas Wogan}, Joshua Krissansen-Totton and David Catling. Abundant atmospheric methane from volcanism on terrestrial planets is unlikely and strengthens the case for methane as a biosignature. \emph{Planetary Science Journal}. \href{https://doi.org/10.3847/PSJ/abb99e}{DOI: 10.3847/PSJ/abb99e}.
\item[2020]
  Kevin Zahnle, Roxana Lupu, David Catling, and \textbf{Nicholas Wogan}. Creation and evolution of impact-generated reduced atmospheres of early Earth. \emph{Planetary Science Journal}. \href{https://doi.org/10.3847/PSJ/ab7e2c}{DOI: 10.3847/PSJ/ab7e2c}.
\item[2020]
  \textbf{Nicholas Wogan} and David Catling. When is chemical disequilibrium in Earth-like planetary atmospheres a biosignature versus an anti-biosignature? Disequilibria from dead to living worlds. \emph{Astrophysical Journal}. \href{https://doi.org/10.3847/1538-4357/ab7b81}{DOI: 10.3847/1538-4357/ab7b81}.
\end{cvlist}

\section{Non-Peer-Reviewed Publications}

\begin{cvlist}
\item[2025]
  \textbf{Nicholas Wogan}, James Mang, Natasha Batalha et al. (2025). The Sonora Substellar Atmosphere Models. V. A Correction to the Disequilibrium Abundance of CO$_2$ for Sonora Elf Owl. \emph{RNAAS}. \href{https://doi.org/10.3847/2515-5172/add407}{DOI: 10.3847/2515-5172/add407}.
\item[2025]
  Sukrit Ranjan, ..., \textbf{Nicholas Wogan} et al. (2025). Prebiosignatures with the Habitable Worlds Observatory (HWO). \emph{HWO Science Case Development Document}. \href{https://doi.org/10.48550/arXiv.2507.00165}{DOI: 10.48550/arXiv.2507.00165}.
\item[2025]
  Sukrit Ranjan, ..., \textbf{Nicholas Wogan} et al. (2025). Testing Origin-of-Life Theories with the Habitable Worlds Observatory (HWO). \emph{HWO Science Case Development Document}. \href{https://doi.org/10.48550/arXiv.2507.00164}{DOI: 10.48550/arXiv.2507.00164}.
\item[2025]
  Theresa Fisher, ..., \textbf{Nicholas Wogan} et al. (2025). Network and Kinetics-based Biosignatures: Implications for the Putative Habitable World Observatory Design. \emph{HWO Science Case Development Document}. \href{https://doi.org/10.48550/arXiv.2501.04737}{DOI: 10.48550/arXiv.2501.04737}.
\item[2024]
  Ella Sciamma-O'Brien, Thomas Drant and \textbf{Nicholas Wogan}. In an exoplanet atmosphere far, far away. \emph{Nature News \& Views}. \href{https://doi.org/10.1038/s41570-024-00586-2}{DOI: 10.1038/s41570-024-00586-2}.
\end{cvlist}

\section{Research and Observing Proposals Awarded}

\begin{cvlist}
\item[2025 - 2026]
  Title: ``The First Set of Documentation and Tutorials for Any Photochemical Exoplanet Code''\\
  PI: Nicholas Wogan\\
  Program: NASA NNH24ZDA001N-SOSS:F.8 Supplements for Open-Source Science\\
  Total budget: \$50,000
\item[2025 - 2028]
  Title: ``Exploring the Influence of Hazes on Climate and Spectra of Small Planets around FGK Stars''\\
  PI: Ravi Kopparapu (NASA Goddard Spaceflight Center)\\
  Program: NASA NNH24ZDA001N-HW:F.4 Habitable Worlds\\
  Total budget: \$484,053
\item[2025 - 2028]
  Title: ``The Other Extreme: Enabling Characterization of Metal-poor Brown Dwarfs and testing our Understanding of Jupiter and Saturn''\\
  PI: Sagnick Mukherjee (Arizona State University)\\
  Program: JWST cycle 4 GO, Exoplanets and Exoplanet Formation\\
  Total budget: Not yet allocated.
\item[2025 - 2028]
  Title: ``Cliff Hangers: Testing for Atmosphere-Mantle Interactions in Radius Cliff Planets''\\
  PI: Natasha Batalha\\
  Program: JWST cycle 4 GO, Exoplanets and Exoplanet Formation\\
  Total budget: Not yet allocated.
\end{cvlist}

\section{Selected Presentations}

\noindent Invited

\begin{cvlist}
\item[2025]
  \textbf{Nicholas Wogan}. The photochemistry and climate of foreign atmospheres: Implications for the origin of life on early earth and understanding exoplanets observed by the James Webb Space Telescope. Planetary Science Seminar, California Institute of Technology.
\item[2024]
  \textbf{Nicholas Wogan}. Workshop on the \texttt{Photochem} code for simulating exoplanet atmospheres. Theoretical Astrophysics Program Planet Formation Initiative Lectureship, University of Arizona.
\item[2024]
  \textbf{Nicholas Wogan}. Assessing exoplanet habitability with JWST and the Habitable Worlds Observatory: from the sub-Neptune K2-18b to rocky Earth-like planets. Planetary lunch, University of California Santa Cruz.
\item[2024]
  \textbf{Nicholas Wogan}. The photochemistry of hydrogen-rich atmospheres: From the origin of life on Earth to biosignatures on the K2-18b exoplanet. Institute for Geophysics and Planetary Physics seminar, University of California Santa Cruz.
\item[2022]
  \textbf{Nicholas Wogan}, David Catling, Kevin Zahnle, and Mark Claire. Rapid timescale for an oxic transition during the Great Oxidation Event and the instability of low atmospheric O$_2$. NASA Goddard Exoplanets Seminar.
\item[2020] 
  \textbf{Nicholas Wogan} and David Catling. Atmospheric synthesis of prebiotic molecules on the Hadean Earth. Prebiotic Chemistry and Early Earth Environments Consortium (PCE3), remote conference.
\end{cvlist}

\noindent Contributed

\begin{cvlist}

\item[2025]
  \textbf{Nicholas Wogan}, Natasha Batalha, Kevin Zahnle, Joshua Krissansen-Totton. Towards a universal chemical and climate model of planetary atmospheres for interpreting HWO observations. Towards the Habitable Worlds Observatory: Visionary Science and Transformational Technology, Washington, D.C.
\item[2025]
  \textbf{Nicholas Wogan}, Natasha Batalha, Kevin Zahnle, Joshua Krissansen-Totton. Towards a general chemical and climate model of planetary atmospheres for interpreting exoplanet observations. Exoclimes, Montreal, Canada.
\item[2025]
  \textbf{Nicholas Wogan}, Natasha Batalha, Joshua Krissansen-Totton, Kevin Zahnle. On inferring the surface production rate of biogenic gases on rocky exoplanets from telescope spectra. American Astronomical Society Meeting, National Harbor, MD.
\item[2024]
  \textbf{Nicholas Wogan}, Natasha Batalha, Joshua Krissansen-Totton, Kevin Zahnle. A self-consistent photochemical-climate-flux retrieval method for exoplanet characterization and life detection. American Geophysical Union Fall Meeting, Washington, D.C.
\item[2024]
  \textbf{Nicholas Wogan}, Natasha Batalha, Kevin Zahnle, Joshua Krissansen-Totton, Shang-Min Tsai and Renyu Hu. JWST observations of K2-18b can be explained by a gas-rich mini-Neptune with no habitable surface. AbSciCon, Providence, RI.
\item[2024]
  \textbf{Nicholas Wogan}, Natasha Batalha, Kevin Zahnle, Joshua Krissansen-Totton and Shang-Min Tsai. JWST observations of K2-18b can be explained by a gas-rich mini-Neptune composition. Extreme Solar Systems V, Christchurch, New Zealand.
\item[2023]
  \textbf{Nicholas Wogan}, David Catling, Kevin Zahnle, and Roxana Lupu. Origin of life molecules in the atmosphere after big impacts on the early Earth. American Geophysical Union Fall Meeting, San Francisco, CA.
\item[2023]
  \textbf{Nicholas Wogan}, Shawn Domagal-Goldman, Chris Stark, Aki Roberge, Giada Arney, Tyler Robinson. Detecting exo-Earths with the Habitable Worlds Observatory. Habitable Worlds Observatory Conference, Baltimore, MD.
\item[2023]
  \textbf{Nicholas Wogan}, David Catling, Kevin Zahnle, and Mark Claire. Rapid timescale for an oxic transition during the Great Oxidation Event and the instability of low atmospheric O$_2$. Green Bank Astrobiology Conference, Green Bank, WV.
\item[2022]
  \textbf{Nicholas Wogan}, David Catling and Kevin Zahnle. Atmospheric nitriles for the origin of life from the atmosphere after large asteroid impacts on the Hadean Earth. Latsis Conference, Zurich, Switzerland.
\item[2022]
  \textbf{Nicholas Wogan}, David Catling and Kevin Zahnle. Origin of life chemistry in the atmosphere after large impacts on the early Earth. Astrobiology Science Conference, Atlanta, GA.
\item[2021]
  \textbf{Nicholas Wogan}, David Catling and Kevin Zahnle. Molecules for the origin of life from impact-generated atmospheres on early Earth. Simons Foundation Collaboration on the Origin of Life Annual meeting, remote conference.
\item[2021]
  \textbf{Nicholas Wogan}, David Catling and Kevin Zahnle. Molecules for the origin of life from impact-generated atmospheres on early Earth. Goldschmidt, remote conference.
\item[2019]
  \textbf{Nicholas Wogan} and David Catling. When is chemical disequilibrium in Earth-like planetary atmospheres a biosignature versus an anti-biosignature? Investigating disequilibria from prebiotic to post-biotic worlds. American Geophysical Union Fall Meeting, San Francisco, CA.
\end{cvlist}

\section{Recent Selected Press}

\begin{cvlist}
\item[2025]
  National Geographic: \href{https://www.nationalgeographic.com/science/article/alien-planet-signs-life-biosignature-exoplanet}{Is there really alien life on this exoplanet? We asked 10 experts.}
\item[2024]
  New Scientist: \href{https://www.newscientist.com/article/2419474-habitable-ocean-world-k2-18b-may-actually-be-inhospitable-gas-planet/}{Habitable ocean world K2-18b may actually be inhospitable gas planet}
\item[2024]
  YouTube, Dr. Becky: \href{https://www.youtube.com/watch?v=r0lGz73rluo}{K2-18b: did JWST really find evidence of life on this exoplanet?}
\item[2023]
  Washington Post: \href{https://www.washingtonpost.com/science/2023/12/19/early-earth-life-impacts-ocean/}{Giant space rock made Earth's ocean boil but also helped early life}
\end{cvlist}

\section{Open Source Software}

\begin{itemize}
  \item Photochem: \url{https://github.com/Nicholaswogan/photochem}. A 1-D photochemical and climate model of planetary atmospheres.
  \item fortran-yaml-c: \url{https://github.com/Nicholaswogan/fortran-yaml-c}. A YAML parser and emitter for Fortran.
  \item Differentia: \url{https://github.com/Nicholaswogan/Differentia}. Forward mode automatic differentiation for Fortran.
  \item numbalsoda: \url{https://github.com/Nicholaswogan/numbalsoda}. A high performance ordinary differential equation solver for Python.
\end{itemize}

\end{document}

